CODECHECK: An open-science initiative for the independent execution of computations underlying research articles.

### 2021-01-10 codecheck-paper.tex
emmy ok

% question mark indicates we are waiting for person to respond.
We are grateful to the following individuals for discussions regarding
the work presented here: Andy Collings, Melissa Harrison?, Giuliano
Maciocci, Naomi Penfold, Emmy Tsang? (eLife), Rebecca Kirk (PLOS
Computational Biology), Scott Edmunds (GigaScience), and Andrew
Hufton? (Scientific Data). Iain Davies and Yuhao (Sebastian) Wang
developed code and example certificates.  We thank Antonio P\'{a}ez?
(Journal of Geographical Systems) for enabling CODECHECKs, Carlos
Granell and Frank Ostermann? for contributing certificates as
reproducibility reviewers at the AGILE conference, and all authors of
auditable workflows for their participation.

>>>>

% question mark indicates we are waiting for person to respond.
We are grateful to the following individuals for discussions regarding
the work presented here: Andy Collings, Melissa Harrison?, Giuliano
Maciocci, Naomi Penfold, Emmy Tsang (eLife), Rebecca Kirk (PLOS
Computational Biology), Scott Edmunds (GigaScience), and Andrew
Hufton? (Scientific Data). Iain Davies and Yuhao (Sebastian) Wang
developed code and example certificates.  We thank Antonio P\'{a}ez?
(Journal of Geographical Systems) for enabling CODECHECKs, Carlos
Granell and Frank Ostermann? for contributing certificates as
reproducibility reviewers at the AGILE conference, and all authors of
auditable workflows for their participation.
